An New Search for Supernova Remnants in NGC\,6946

### 2019-01-07 ms.tex
Updates from ShareLaTeX
Updated version on Overleaf

\documentclass[modern]{aastex62}
%\documentclass{aastex5}

%%
%% using aastex version 6.1

@@

\title{An Expanded Search for Supernova Remnants in NGC\,6946}

@@

\correspondingauthor{Knox S Long}
\email{long@stsci.edu}

@@

The relatively nearby spiral galaxy NGC~6946 is one of the most actively star forming galaxies in the local Universe.  Nine supernovae have been observed since 1917 and as a result NGC~6946 must contain a large number of supernova remnants.  Here we report a new optical search for supernova remnants in NGC~6946.  Specifically, we have identified 147 emission nebulae in NGC~6946 as likely supernova remnants based on the fact that they have elevated \sii:\ha\ ratios compared to \hii\ regions in narrow band images obtained with the WIYN telescope.  We then obtained spectra of 102 of these emission nebulae with Gemini North/GMOS; of these 89 have \sii:\ha\ ratios greater than 0.4, the criterion for establishing an emission nebulae as a supernova remnant.  All but one of the 27 SNR candidates identified earlier by Matonick \& Fesen (1997) are contained in our sample.  However, there is very little overlap in our sample between the supernova remnant candidates identified by Bruursema et al. (2014) from \feii\ imagery or by Lacey et al. (2001) from radio data.  Very few of the supernova remnant candidates are X-ray sources, unlike the situation in some other galaxies such as M33 and M83, possibly due to the fact that there is more reddening along the line of sight to NGC~6946 than these galaxies.  The emission line ratios, e.g., of \nii:\ha\ of the candidates in NGC~6946 are fairly typical of those observed in SNRs in samples of other galaxies with comparable metallicity.  None of the historical supernovae were detected as supernova remnants and none of the candidates show evidence of anomalous abundances suggestive of ejecta material or  significant velocity broadening in our low resolution spectra.

@@

@@

\gal\ is a nearby \cite[6.72$\pm$ 0.15 Mpc,][]{tikhonov14}, nearly face-on \cite[i = 32.6$\degr$,][]{deblok08} galaxy with four flocculent spiral arms.  The galaxy is currently undergoing a major starburst, and as a result it has been the site of ten historical supernovae (SNe) since 1917, the most of any known galaxy. According to \citet{jarrett13} the total star formation rate is $3.2\, M_\sun\,{\rm yr}^{-1}$, a high rate that is thought to be bar-driven.  A total of 121 bubbles, probably created by stellar winds and multiple SNe at the star-formation sites have been identified in \hi\ gas that extends well outside the bright portions of the optical galaxy \citep{boomsma08}.  %The high SFR in \gal\ is thought to be bar-driven.   
Given these properties, one expects that a large number of supernova remnants (SNRs) should be present in \gal\ since SNRs tend to remain visible for thousands of years.

Optically, SNRs are usually identified on the basis of high \sii:\ha\ ratios compared to \hii\ regions.  In bright \hii\ regions, most S is found in the form of S$^{++}$ or S$^{+++}$, and as a result the \sii:\ha\ ratios are typically 0.1 or smaller.  In SNRs, where emission is shock driven, S$^+$ is found in an extended recombination and cooling zone behind the shock and the \sii:ha\ ratios are typically $\geq$0.4.  The situation becomes more complicated in lower surface brightness \hii\ regions, as recently discussed by \cite{long18} for the case of M33.

The first optical search for SNRs in \gal\ was made by \cite{matonick97}, hereafter MF97, who used interference filter imagery to identify 27 emission nebulae with \sii:\ha\ ratios $\geq$ 0.45 as SNRs.  One of these sources, MF97-16, was, later associated with the Ultraluminous Black Hole X-ray binary NGC6946 X-1 \cite{roberts03}. Though very rare, ULXs have  the hard X-ray spectra that produce line ratios in the surrounding circumstellar ISM that resemble that expected of SNRs. To our knowledge, no other optical searches for SNRs in NGC~6946 exist, nor have spectra of the remaining MF97 objects ever been obtained.

\hii\ regions and SNRs also radiate at radio wavelengths.  SNRs typically have steep non-thermal spectra arising from synchrotron radiation whereas \hii\ regions have (flat) thermal spectra arising from free-free and recombination radiation (check).  At radio wavelengths, SNRs in nearby galaxies are generally identified as non-thermal radio sources associated with optical \ha\ emission, that latter requirement arising because many background radio sources also have non-thermal spectra and because generally the SNRs are unresolved in galaxies beyond the Local Group.  In the case of \gal,  \cite{lacey01} identified 35 radio-selected SNR candidates on the basis of these criteria, none of which overlap with the MF97 list of optical candidates.  Their radio candidates were located in the brightest parts of the spiral arms of \gal\ and they suggested that the reason the two lists do not overlap is primarily due to selection effects.

Here we discuss a new, more sensitive optical search for SNRs in \gal\ in which we identify a total of 147 SNR candidates using interference filter imagery.  We also discuss spectroscopic observations of 102 of these candidates, which we use to verify the ratios obtained from the imaging and to characterize other characteristics of our new optical sample.

\section{Observations and Data Reduction \label{sec:observations}}
\subsection{Imaging}

We carried out narrow-band imaging observations of \gal\ from the 3.5m WIYN telescope and MiniMosaic imager on Kitt Peak on the nights of 2011 June 26-28 (UT).  The so-called ``Minimo'' was mounted at the f/6.3 Nasmyth port and consisted of a pair of $2048\times4096$ SITe chips, with a field  9\farcm 6 square at a scale of 0\farcs 14 pixel$^{-1}$.  We used interference filters that pass lines of \ha, \sii \lamlam6716,6731, and \oiii \lam 5007, plus red and green continuum filters so we could subtract the stars and produce pure emission-line images. Images in each filter were dithered to enhance removal of cosmic rays and bad pixels.  Further observational details are given in Table 1.  It is noteworthy that the \ha\ filter has quite a narrow bandwidth, 27\ \AA\ FWHM. Its transmission is 69\% at the rest wavelength of \ha, but only 11\% at 6548\ \AA\ and 16\% at 6583\ \AA; hence, the \nii\ lines are greatly attenuated relative to \ha.\footnote{The recessional velocity of \gal\ is only $40 \kms$, so the lines are redshifted by $\lesssim 1$ \AA.}  This facilitates identification of SNRs based on their image-derived \sii:\ha\ ratios.

\todo[inline]{WPB: Add something in above paragraph indicating what the effective seeing was.  Or add to Table 1, if it varied enough between filters to make it worthwhile.}

We used standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} techniques for processing the images, including overscan correction, bias subtraction, and flat-fielding using dome flats.  Procedures in the IRAF {\texttt mscred} package were then used to combine the data from the individual chips into a mosaic image for each frame, assigned a WCS for each using stars from the USNOB1 catalog, and then stacked  all the images by   filter onto an arbitrary standard coordinate system with a scale of 0\farcs 20 pixel$^{-1}$.  We then scaled and subtracted the continuum images from the emission-line ones (red from \ha\ and \sii; green from \oiii) to give pure emission-line images with most of the stars and galaxy background light removed.  Finally, we used observations of several spectrophotometric standard stars from the catalog of \citet{massey88} to flux calibrate the emission-line images.  Figure \ref{fig_overview} shows a color version of the final images (R = \ha, G = \sii, B = \oiii).

@@

To select SNR candidates, we displayed continuum-subtracted WIYN images in all three emission lines, as well as \sii:\ha\  and \oiii:\ha\ ratio images, and a continuum image (to distinguish stars  or stellar subtraction residuals from point-like nebulae), all in DS9.   We then visually inspected these to select SNR candidates based on a high  \sii:\ha\ ratio.  The initial inspection was carried out by Middlebury undergraduate Marc DeLaney; subsequently two of us (WPB and PFW) conducted independent inspections, and then we conferred to agree on a consensus list of 147 candidates, including the 27 from MF97.   In addition, we selected 51 candidates with relatively high \oiii:\ha\ ratios, in an attempt to identify young, ejecta-dominated SNRs such as Cas A in the Galaxy. With ten SNe in the last century, one might expect a number of young, ejecta-dominated SNRs to be present.  Though none of the O-selected candidates had ratios as extreme as seen for Cas A or 1E0102-72.3 in the Small Magellanic Cloud, we nevertheless selected some of these for follow-up spectroscopy.  Finally, we inspected the positions of all nine\footnote{As of the 2011 observations; a tenth SN was recorded in 2017.} historical SNe in \gal\ for evidence of nebular emission.

\todo[inline]{Note which of these have detected optical emission.  Also, add symbols to Fig. 1 overview and reference the Figure again here?  I note below we intend to also indicate those observed spectroscopically with a separate symbol or different color.  Could be tricky. WPB}

The SNR candidates are listed in Right Ascension order in Table \ref{table_candidates}.  For each candidate, we provide (1) a source name, (2) the name of the source in MF97 if any,  (3,4) the position  (J2000), (5) the galactocentric distance (GCD), (6) the \ha\ flux as derived from the emission line images, (7) the \sii:\ha\ ratio measured from the images, (8) the spectrum we used to confirm the imaging ratios (see below), and (9) whether or not the object has a spectroscopic confirmation that the  \sii:\ha\ ratio is $\ge$ 0.4 (see below).

\subsection{Spectroscopy}

@@

We used the Gemini Multi-Object Spectrograph (GMOS) on the 8.2m Gemini-North telescope to obtain all the spectra reported here, during queue-scheduled programs in semesters 2014B (program GN-2014B-Q-83) and 2015B (program GN-2015B-Q-91).  
For the 2014B program, we designed six custom masks, each with 20-30 slitlets targeting SNR candidates whose positions we determined from our 2011 WIYN images, together with  short $R$-band pre-images of several \gal\ fields taken with GMOS earlier in 2014 as part of the spectroscopy preparation program.    
We used two additional masks (which we refer to as masks 7 and 8 for simplicity)  for the 2015B program.
%For both programs we selected objects from the lists of SNR candidates in D10 and in a preliminary version of the catalog that later appeared in B12.
 %([based on our 2009 Magellan IMACS images) and D10, based on WFC3 images.
 Slitlets in one or more of our eight masks were placed on 102 distinct SNR candidates, including ones with a range of sizes, GCDs, and ISM environments (locations in arms and in 
inter-arm regions).  In addition to the SNR candidates, we also placed a number of slitlets on prominent \hii\ regions for comparison purposes in both 2014 and 2015.
 %\footnote{Exceptions are the very outermost regions of the galaxy, where the sparse population would have made less efficient use of the $5\farcm 5 \times 5\farcm 5$ GMOS field, and the innermost nuclear region, where source confusion and the high star density would have made sky subtraction difficult.}  
Figure \ref{fig_overview} shows all the objects from the sample for which we obtained spectra (red boxes).

For all the spectra we used GMOS-N with the 600 line\,mm$^{-1}$ grating designated G5307 and a GG455 cut-off filter to block second-order spectra.   The detector in both years was a mosaic of three e2v deep depletion CCD chips, binned by 2 in the spatial direction (for a scale of 0\farcs 146 pixel$^{-1}$) and by 4 in the dispersion direction.  
The dispersion was 1.84 \AA\,  pixel$^{-1}$ (binned), resulting in coverage of the spectral range fromn at least \hb\ through \sii\lamlam 6716,\,6731 for virtually all the objects.\footnote{The detailed wavelength coverage for individual objects naturally varied with slitlet position in the dispersion direction.}  Our  masks had  slitlet  widths from 1\farcs 25 to 1\farcs 75, with wider slits used for the larger objects, and lengths of 6\arcsec\ or longer to permit local background and sky subtraction.

@@

\todo[inline]{WPB: Next paragraph: Frank, do we need to say something about how the separate grating offset exposures were shifted and co-added prior to obtaining the final 2-D spectra for each slitlet?}

The data were processed using standard procedures for bias subtraction, flat-fielding, wavelength calibration, and flux calibration (based on baseline GMOS observations of a few spectrophotometric standard stars) from the {\tt gemini} package in IRAF.
%  IRAF footnote already given above, so I commented this out.  WPB
%\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.}  
During the processing, the 2-D spectra from different slitlets were separated to give individual 2-D spectra from each slitlet.   We examined each of these individually and selected the object region, as well as one or more sky background regions,  stripped out 1-D spectra of each, and then subtracted the sky spectrum from the corresponding object to obtain the final object spectra.
Many of the objects are located in regions with bright surrounding galactic background (both continuum and emission lines) from NGC\,6946, so the ability to choose a representative  local background was often a source of uncertainty.  
We then performed  fits to obtain emission line fluxes  from the spectra.  For these fits, we assumed Gaussian profiles.  We performed fits for various lines and line complexes, specifically for \hb\ alone, for the \oiii\ doublet, for the \oi\ doublet, for the \ha-\nii\ region, and  for the \sii\ doublet. For the fits, we assumed that the background varied linearly with wavelength around each line, and that the FWHM of the lines in each line in a complex was the same.

@@

Table \ref{table_snr_spec}  lists the information we obtained for the SNR candidates for which we obtained spectra.  Specifically we list (1) the source name, (2) the extracted  \ha\ flux, (3-9) ratios of various emission lines to \ha\ taken to be 300, (10) the total \sii:\ha\ ratio and (11) the measured FWHM of the lines in the \ha-\nii\ complex.  For doublets, where the line ratio is constrained by atomic physics, that is \oiii, \oi, and \nii, we have listed only the stronger line.  We visually inspected all of the spectra and the fits to them; values which we judge to be more uncertain are shown as approximate.  No allowance has been made for systematic errors associated with difficulties in background subtraction.  A number of the objects were observed several times, sometimes with different slit orientations.  In these cases, we used the spectrum which we judged to be the most accurate and report it for reference in the `Spectrum' column in Table \ref{table_candidates}, where (for example) 05.18 should be interpreted as `mask 5 slitlet number 18.'

@@

We identified 147 candidate SNRs from the WIYN interference images; of these we obtained spectra of 102. The spectra were needed to improve our confidence that the \sii:\ha\ ratios of the emission nebulae were indeed high and to begin to characterize the SNRs.  The spectroscopic ratios are shown as a function of GCD in the left panel of  Fig.\ \ref{fig_s2_ha}. \hii\ regions and \oiii-selected objects are shown in blue while nominal \sii:\ha\ candidates from imaging are shown in red.   Conventionally, emission nebulae are identified as SNRs optically, if the \sii:\ha\ ratio exceeds 0.4; 89 of the 102 SNRs with spectra satisfy this criterion, and so we regard these as confirmed SNRs (and they have been listed as such in Table \ref{table_candidates}. Clearly, given uncertainties in derived line ratios for faint emission line objects, a dividing line of 0.4 is somewhat arbitrary, and objects just above (or just below) this ratio should be judged with more context.  For example, slightly under-subtracting contaminating \ha\ emission could readily explain why some candidates ended up below the threshold in the spectroscopic analysis. Likewise, a slight over-subtraction of \ha\ could enhance the \sii:\ha\ ratio derived, potentially pushing some objects above the threshold.  The observed tendency to see higher \sii:\ha\ ratios closer to the nucleus is likely to be at least partly an abundance effect; similar trends are seen in M33 \citep{long18} and in M83 \citep{winkler17}.

There are 45 objects without spectra, so which of these are actually SNRs is uncertain.  That said, as shown in the right panel of Fig.\ \ref{fig_s2_ha}, if anything the spectroscopically-determined ratios tend to be higher than the ratios determined from narrow band imaging, and so most of the objects without spectra are also likely to be SNRs.  The somewhat higher spectroscopic ratios are to be expected, since the \ha\ filter also passed some emission from \nii.

Of the 27 SNR candidates identified by MF97, all have imaging \sii:\ha\ ratios that exceed 0.4. MF97 obtained spectra of six of their candidates.  We have obtained spectra of 23 of the MF97 objects, including new spectra of the 5 objects for which MF97 had spectra. Four -- MF003, MF021, MF022, and MF026 -- were observed spectroscopically.  All of these have measured spectroscopic ratios that exceed 0.4.

\todo[inline]{We need a more complete discussion of MF97 and our results.  Possibly this is something wpb could do.  WPB: possibly, if it can wait until I return.  The above paragraph says both "4" and "5" MF objects were observed spectroscopically, so this needs to get cleaned up.}

\todo[inline]{Add comparison here to X-ray sources and to radio SNRs from earlier Lacey paper and also Bruursema+ (2014)}

As shown in Fig.\ \ref{fig_s2_ratio}, the ratios of [SII]$\lambda$6717:SII]$\lambda$6731 for the SNR candidates cluster around the low density limit of 1.4, and from the fact that just about as many objects have nonphysical ratios above 1.4 as below, suggests that the all of the objects are close to this limit.  In the absence of SNR dieameters, we cannot search for trends with diameter, as were seen in M33 (L18) and M83 \citep{winkler17}.

\hb:\ha\ ratios of the SNR candidates with spectra are shown in Fig.\ \ref{fig_reddening} as a function of GCD. Nearly all of the SNRs show significant reddening, as one would expect since, at 12\degr\ from the Galactic plane, reddening from within our Galaxy along the line of sight is expected to be E(B-V) = 0.29 \citep{schlafly11}.  There is clearly substantial internal reddening  within \gal\ as well, as there is a very evident trend for objects near the center of \gal\ to be more reddened than those more distant from the nucleus.

\todo[inline]{Bill and Frank point out that various other diagrams with GC radius are missing, and in particular \sii:\ha\ ratio vs. \ha\ flux; \sii:\ha\ ratio vs. GCD (fig for this already here)  Check M83 to see if there is a correlation in the spectroscopic ratio with GCD, and if so comment on this.  This is done for S2; I guess we could to it for N2. Gradients: \nii:\ha\ and \sii:\ha\ vs GCD (M83 paper, fig 8) [WPB: Yes, I'd definitely like to see what this looks like.]}

>>>>

\documentclass[modern]{aastex62}

%%
%% using aastex version 6.2

@@

\title{An New Search for Supernova Remnants in NGC\,6946}

@@

\correspondingauthor{Knox S. Long}
\email{long@stsci.edu}

@@

The relatively nearby spiral galaxy NGC~6946 is one of the most actively star forming galaxies in the local Universe.  Ten supernovae have been observed since 1917, and hence NGC~6946 surely contains a large number of supernova remnants (SNRs).  
Here we report a new optical search for these SNRs in NGC~6946 using narrow-band images obtained with the WIYN telescope to 
identify 147 emission nebulae 
as likely SNRs,  based on elevated \sii:\ha\ ratios compared to \hii\ regions.  We have obtained spectra of 102 of these emission nebulae with Gemini North--GMOS; of these, 89 have \sii:\ha\ ratios greater than 0.4.  All but one of the 27 SNR candidates identified earlier by Matonick \& Fesen (1997) are contained in our sample.  However, there is very little overlap in our sample between the SNR candidates identified by Bruursema et al. (2014) from \feii\ imagery or by Lacey et al. (2001) from radio data.  Very few of the SNR candidates are X-ray sources, unlike the situation in some other galaxies such as M33 and M83, possibly due to  more reddening along the line of sight to NGC~6946.  The emission line ratios, e.g., \nii:\ha\ of the candidates in NGC~6946 are fairly typical of those observed in SNR samples from other galaxies with comparable metallicity.  
Two of the historical supernovae were detected as young optical SNRs showing high velocity ejecta. None of the other candidates observed spectroscopically show evidence of anomalous abundances or evidence of significant velocity broadening in our low resolution spectra.

@@

\todo[inline]{WPB: This will likely have to get shortened further before submission.}

@@

\gal\ is a nearby \cite[$6.72\pm 0.15$ Mpc,][]{tikhonov14}, nearly face-on \cite[$i = 32.6\degr$,][]{deblok08} galaxy with four flocculent spiral arms.  The galaxy is currently undergoing a major starburst, and as a result it has been the site of ten historical supernovae (SNe) since 1917, the most of any known galaxy. According to \citet{jarrett13} the total star formation rate is $3.2\, M_\sun\,{\rm yr}^{-1}$, a high rate that is thought to be bar-driven.  A total of 121 bubbles, probably created by stellar winds and multiple SNe at the star-formation sites, have been identified in \hi\ gas that extends well outside the bright portions of the optical galaxy \citep{boomsma08}.  %The high SFR in \gal\ is thought to be bar-driven.   
Given these properties, one expects that a large number of supernova remnants (SNRs) should be present in \gal, since SNRs tend to remain visible for thousands of years.

Optically, SNRs are usually identified on the basis of high \sii:\ha\ ratios compared to \hii\ regions.  In bright \hii\ regions, most S is found in the form of S$^{++}$ or S$^{+++}$, and as a result the \sii:\ha\ ratios are typically 0.1 or smaller.  In SNRs, where emission is driven by impulsive heating from shock waves, S$^+$ is found in an extended recombination and cooling zone behind the shock, and the \sii:\ha\ ratios are typically $\gtrsim0.4$.  The diagnostic can become less deterministic at lower surface brightness, as recently discussed by \cite{long18} for the case of M33.

The first optical search for SNRs in \gal\ was made by \cite{matonick97}, hereafter MF97, who used interference filter imagery to identify 27 emission nebulae with \sii:\ha\ ratios $\geq$ 0.45 as SNRs.  One of these sources, MF97-16, was, later associated with the ultraluminous black hole X-ray binary NGC~6946 X-1 \citep{roberts03}. Though very rare, such ultra-luminous X-ray sources (ULXs) have  the hard X-ray spectra that produce line ratios in the surrounding circumstellar ISM that resemble those expected from SNRs. To our knowledge, no other optical searches for SNRs in NGC~6946 exist, nor have spectra of the remaining MF97 objects ever been reported.

\hii\ regions and SNRs also radiate at radio wavelengths.  SNRs typically have steep non-thermal radio spectral indices arising from synchrotron radiation, whereas \hii\ regions have relatively flat thermal spectra arising from free-free and recombination radiation. \todo{KSL to check previous assertion}  At radio wavelengths, SNRs in nearby galaxies are generally identified as non-thermal radio sources associated with optical \ha\ emission.  (This association criterion arises because many background radio sources---typically active galaxy nuclei (AGNs)---also have non-thermal spectra, and like AGNs, the SNRs are generally unresolved in radio images of galaxies beyond the Local Group.)  In the case of \gal,  \cite{lacey01} identified 35 radio-selected SNR candidates on the basis of these criteria, none of which overlap with the MF97 list of optical candidates.  Their radio candidates were located in the brightest parts of the spiral arms of \gal; Lacey \& Duric suggested that the reason the two lists do not overlap is primarily due to selection effects.

Here we discuss a new, more sensitive optical search for SNRs in \gal\ in which we identify a total of 147 SNR candidates using interference filter imagery.  We also discuss spectroscopic observations of 102 of these candidates, which we use to verify the ratios obtained from the imaging and to characterize other characteristics of our new optical sample.  The paper is organized as follows:  Section 2 describes both our imaging and spectroscopy observations,  presents our much-expanded catalog of optical SNR candidates, and the results of our spectroscopy that has confirmed many of these.  Section 3 discusses these results in the context of both \gal\ and other spiral galaxies, and Section 4 provides a brief summary of our results.

\section{Observations and Data Reduction \label{sec:observations}}
\subsection{Imaging and Catalog of SNR Candidates}

We carried out narrow-band imaging observations of \gal\ from the 3.5m WIYN telescope and MiniMosaic imager on Kitt Peak on the nights of 2011 June 26-28 (UT).  The so-called ``Minimo'' was mounted at the f/6.3 Nasmyth port and consisted of a pair of $2048\times4096$ SITe chips, with a field  9\farcm 6 square at a scale of 0\farcs 14 pixel$^{-1}$.  We used interference filters that pass lines of \ha, \sii \lamlam6716,6731, and \oiii \lam 5007, plus red and green narrow-band continuum filters so we could subtract the stars and produce pure emission-line images. Frames in each filter were dithered to enhance removal of cosmic rays and bad pixels.  Further observational details are given in Table 1.  It is noteworthy that the \ha\ filter has quite a narrow bandwidth, 27\ \AA\ FWHM. Its transmission is 69\% at the rest wavelength of \ha, but only 11\% at 6548\ \AA\ and 16\% at 6583\ \AA; hence, the \nii\ lines are greatly attenuated relative to \ha.\footnote{The recessional velocity of \gal\ is only $40 \kms$, so the lines are redshifted by $\lesssim 1$ \AA.}  This facilitates identification of SNRs based on their image-derived \sii:\ha\ ratios.  Seeing throughout this run was about $1\arcsec \approx 32$ pc at the distance of \gal.  While sufficient for identifying SNRs in all but the most crowded regions, this resolution could provide only crude diameter estimates and only for the larger objects.

We used standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} techniques for processing the images, including overscan correction, bias subtraction, and flat-fielding using dome flats.  Procedures in the IRAF {\texttt mscred} package were then used to combine the data from the individual chips into a mosaic image for each frame, assigned a WCS for each using stars from the USNOB1 catalog (WPB: ref needed?).  We then stacked  all the images by filter onto an arbitrary standard coordinate system with a scale of 0\farcs 20 pixel$^{-1}$ and scaled and subtracted the continuum images from the emission-line ones (red from \ha\ and \sii; green from \oiii) to give pure emission-line images with most of the stars and galaxy background light removed.  Finally, we used observations of several spectrophotometric standard stars from the catalog of \citet{massey88} to flux calibrate the emission-line images.  Figure \ref{fig_overview} shows a color version of the final images (R = \ha, G = \sii, B = \oiii).

@@

To select SNR candidates, we used the DS9 display program to show the continuum-subtracted WIYN images in all three emission lines, as well as \sii:\ha\  and \oiii:\ha\ ratio images, and a continuum image (to distinguish stars  or stellar subtraction residuals from point-like nebulae).   We then visually inspected these to select SNR candidates based on a high  \sii:\ha\ ratio.  The initial inspection was carried out by Middlebury undergraduate Marc DeLaney; subsequently two of us (WPB and PFW) conducted independent inspections, and then we conferred to agree on a consensus list of 147 candidates, including the 27 from MF97.   In addition, we selected 51 objects with relatively high \oiii:\ha\ ratios, in an attempt to identify young, ejecta-dominated SNRs such as Cas A in the Galaxy. With ten SNe in the last century, one might expect a number of young, ejecta-dominated SNRs to be present.  Though none of the O-selected candidates had ratios as extreme as seen for Cas A or 1E0102-72.3 in the Small Magellanic Cloud, we nevertheless selected some of these for follow-up spectroscopy.  Finally, we inspected the positions of the nine\footnote{As of the 2011 observations there were nine SNe; a tenth SN was recorded in 2017.} historical SNe in \gal\ for evidence of nebular emission, and detected line emission only at the positions of SN1980K and SN2004et, both of which we targeted for follow-up spectra.

\todo[inline]{Add symbols to Fig. 1 overview and reference the Figure again here?  I note below we intend to also indicate those observed spectroscopically with a separate symbol or different color.  Could be tricky. WPB}

The SNR candidates are listed in Right Ascension order in Table \ref{table_candidates}.  For each candidate, we provide (1) a source name, (2) the name of the source in MF97 if any,  (3,4) the position  (J2000), (5) the deprojected galactocentric distance (GCD), (6) the \ha\ flux as derived from the emission line images, (7) the \sii:\ha\ ratio measured from the images, (8) the spectrum we used to confirm the imaging ratios (see below), and (9) whether or not the object has a spectroscopic confirmation that the  \sii:\ha\ ratio is $\ge$ 0.4 (see below).

\subsection{Spectroscopy; Emission-Line Fluxes}

@@

We used the Gemini Multi-Object Spectrograph (GMOS) on the 8.2m Gemini-North telescope to obtain all the spectra reported here, during queue-scheduled programs in semesters 2014B (program GN-2014B-Q-83) and 2015B (program GN-2015B-Q-91).  
For the 2014B program, we designed six custom masks, each with 20-30 slitlets targeting SNR candidates whose positions we determined from our 2011 WIYN images, together with  short $R$-band pre-images of several \gal\ fields taken with GMOS earlier in 2014 as part of the spectroscopy preparation program.    
We used two additional masks (which we refer to as masks 7 and 8 for simplicity)  for the 2015B program.  Slitlets in one or more of our eight masks were placed on 102 distinct SNR candidates, including ones with a range of sizes, GCDs, and ISM environments (locations in arms and in 
inter-arm regions).  In addition to the SNR candidates, we also placed a number of slitlets on prominent \hii\ regions for comparison purposes in both 2014 and 2015.
Figure \ref{fig_overview} shows all the objects from the sample for which we obtained spectra (red boxes).

For all the spectra we used GMOS-N with the 600 line\,mm$^{-1}$ grating designated G5307 and a GG455 cut-off filter to block second-order spectra.   The detector in both years was a mosaic of three e2v deep-depletion CCD chips, binned by 2 in the spatial direction (for a scale of 0\farcs 146 pixel$^{-1}$) and by 4 in the dispersion direction.  
The dispersion was 1.84 \AA\,  pixel$^{-1}$ (binned), resulting in coverage of the spectral range from at least \hb\ through \sii\lamlam 6716,\,6731 for virtually all the objects.\footnote{The detailed wavelength coverage for individual objects naturally varied with slitlet position in the dispersion direction.}  Our  masks had  slitlet  widths from 1\farcs 25 to 1\farcs 75, with wider slits used for the larger objects, and lengths of 6\arcsec\ or longer to permit local background and sky subtraction.

@@

%\todo[inline]{WPB: Next paragraph: Frank, do we need to say something about how the separate grating offset exposures were shifted and co-added prior to obtaining the final 2-D spectra for each slitlet?}

The data were processed using standard procedures  from the {\tt gemini} package in IRAF  for bias subtraction, flat-fielding, wavelength calibration, and combination of spectra with different grating tilts to provide the final results.  
Flux calibration was based on baseline GMOS observations of a few spectrophotometric standard stars, carried out in the same semester as part of standard GMOS operations.  
%  IRAF footnote already given above, so I commented this out.  WPB
%\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.}  
During the processing, the 2-D spectra from different slitlets were separated to give individual 2-D spectra from each slitlet.   We examined each of these individually and selected the object region, as well as one or more sky background regions,  stripped out 1-D spectra of each, and then subtracted the sky spectrum from the corresponding object to obtain the final background-subtracted object spectra.
Many of the objects are located in regions with bright surrounding galactic background (both continuum and emission lines) from NGC\,6946, so the selection of a representative local background was done on a best-effort basis.  
We then performed  fits to obtain emission line fluxes  from the spectra, assuming Gaussian profiles.  We performed fits for various lines and line complexes:  \hb\ alone,  the \oiii\ doublet,  the \oi\ doublet,  the \ha-\nii\ region, and   the \sii\ doublet. For the fits, we assumed that the background varied linearly with wavelength around each line, and that the FWHM of all lines in each complex was the same.

@@

Table \ref{table_snr_spec}  lists the information we obtained for the SNR candidates for which we obtained spectra.  Specifically we list (1) the source name, (2) the extracted  \ha\ flux, (3-9) ratios of various emission lines to \ha\ [taken to be 300], (10) the total \sii:\ha\ ratio and (11) the measured FWHM of the lines in the \ha-\nii\ complex.  For doublets, where the line ratio is constrained by atomic physics, that is \oiii, \oi, and \nii, we have listed only the stronger line.  We visually inspected all of the spectra and the fits to them; values which we judge to be more uncertain are indicated with tildes.  No allowance has been made for additional errors associated with difficulties in background subtraction.  A number of the objects were observed several times, sometimes with different slit orientations.  In these cases, we used the spectrum which we judged to be the most accurate and report it for reference in the `Spectrum' column in Table \ref{table_candidates}, where (for example) 05.18 should be interpreted as `mask 5 slitlet number 18.'

@@

We identified 147 candidate SNRs from the WIYN interference images; of these we obtained spectra of 102. The spectra were needed to improve our confidence that the \sii:\ha\ ratios of the emission nebulae were indeed high and to begin to characterize the SNRs using accurate line ratios.  The spectroscopic ratios are shown as a function of GCD in the left panel of  Fig.\ \ref{fig_s2_ha}. \hii\ regions and \oiii-selected objects are shown in blue while nominal \sii:\ha\ candidates from imaging are shown in red.   Conventionally, emission nebulae are identified as SNRs optically, if the \sii:\ha\ ratio exceeds 0.4; 89 of the 102 SNRs with spectra satisfy this criterion, and so we regard these as confirmed SNRs (and they have been listed as such in Table \ref{table_candidates}. Clearly, given uncertainties in derived line ratios for faint emission line objects, a dividing line of 0.4 is somewhat arbitrary, and objects just above (or just below) this ratio should be judged with more context.  For example, slightly under-subtracting contaminating \ha\ emission could readily explain why some candidates ended up below the threshold in the spectroscopic analysis. Likewise, a slight over-subtraction of \ha\ could enhance the \sii:\ha\ ratio derived, potentially pushing some objects above the threshold.  The observed tendency to see higher \sii:\ha\ ratios closer to the nucleus is likely to be at least partly an abundance effect; similar trends are seen in M33 \citep{long18} and in M83 \citep{winkler17}.

There are 45 objects without spectra, so which of these are actually SNRs is uncertain.  That said, as shown in the right panel of Fig.\ \ref{fig_s2_ha}, if anything the spectroscopically-determined ratios tend to be higher than the ratios determined from narrow band imaging, and so most of the objects without spectra are also likely to be SNRs.  The somewhat higher spectroscopic ratios are to be expected, since even with our relatively narrow \ha\ filter , some emission from \nii\ was  also passed.

Of the 27 SNR candidates identified by MF97, all have imaging \sii:\ha\ ratios that exceed 0.4. MF97 obtained spectra of six of their candidates.  We have obtained spectra of 23 of the MF97 objects, including new spectra of four objects for which MF97 had spectra -- MF003, MF021, MF022, and MF026.  All of these indeed have measured spectroscopic ratios that exceed 0.4.

\todo[inline]{We need a more complete discussion of MF97 and our results. MF-016 probably needs several sentences as it is a unique object. Possibly this is something wpb could do.  WPB: possibly, if it can wait until I return.}

As shown in Fig.\ \ref{fig_s2_ratio}, the ratios of [S~II]$\lambda$6717:S~II]$\lambda$6731 for the SNR candidates cluster around the low density limit of 1.4, and from the fact that just about as many objects have non-physical ratios above 1.4 as below, suggests that the all of the objects are close to this limit.  In the absence of SNR diameters, we cannot search for trends with diameter, as were seen in M33 (L18) and M83 \citep{winkler17}. Upcoming {\it Hubble Space Telescope} observations will provide accurate diameter information for many of these objects.

Fig.\ \ref{fig_reddening} shows the observed \hb:\ha\ ratios of the SNR candidates with spectra as a function of GCD. Nearly all of the SNRs show significant reddening, as one would expect since, at 12\degr\ from the Galactic plane, foreground reddening from within our Galaxy along the line of sight is expected to be E(B-V) = 0.29 \citep{schlafly11}.  There is clearly substantial internal and differential reddening  within \gal\ as well, as there is a very evident trend for objects near the center of \gal\ to be more reddened than those more distant from the nucleus.

\todo[inline]{Bill and Frank point out that various other diagrams with GC radius are missing, and in particular \sii:\ha\ ratio vs. \ha\ flux; \sii:\ha\ ratio vs. GCD (fig for this already here)  Check M83 to see if there is a correlation in the spectroscopic ratio with GCD, and if so comment on this.  This is done for S2; I guess we could to it for N2. Gradients: \nii:\ha\ and \sii:\ha\ vs GCD (M83 paper, fig 8) [WPB: Yes, I'd definitely like to see what this looks like.].  ksl: This is now provided, but whether these should be included is open to question.  If they are included some massaging of the plots is needed.  If included, Bill or Frank should provide words, and comparison to other galaxies}
